FraCaS: Temporal Analysis

### 2020-06-26 paper2020/paper.tex
typography

For the purpose of this paper, the important point is that the GF
syntax aims at a balance of sufficient abstraction to provide a
semantically-relevant structure, but at the same time it embeds
sufficiently many syntactic features to be able to reconstruct
natural-language text. That is, the parse trees generally satisfy the
homomorphism requirement of \citet{montague_english_1970,montague_proper_1974}, and
we can focus on the translation of syntactic trees to logical forms.
\cref{ex:nobel} shows an example abstract syntax tree and its
realisation in English.

@@

This temporal context is an \emph{optional} timespan. That is, it can
be a timespan or an explicitly unspecified context.
\newcommand\nospan{\ensuremath{-}}
\newcommand\anyspan{\ensuremath{\mathbf{?}}}\todo{better notation} The timespan in the context is
optional because, in certain situations, the semantics is different
depending on whether a timespan has been specified externally or not,
as we explain below. A non-present timespan will be represented as
\nospan{}. If a semantic function does not depend on the temporal
context at all, we will write \anyspan{} instead.

@@

\newcommand\varid[1]{\mathnormal{#1}}
%
The principal non-trivial manipulators of timespans are tense
markers. In our syntax, inherited from GF, tenses are represented
syntactically as an attribute of clauses. An illustration of a
past-tense clause and its interpretation follows in
\cref{ex:nobel}. Notice in particular the $\varid{past}$ argument to
the $\varid{useCl}$ constructor.

>>>>

For the purpose of this paper, the important point is that the GF
syntax aims at a balance of sufficient abstraction to provide a
semantically-relevant structure, but at the same time it embeds
sufficiently many syntactic features to be able to reconstruct
natural-language text. That is, the parse trees generally satisfy the
homomorphism requirement of \citet{montague_english_1970,montague_proper_1974}, and
we can focus on the translation of syntactic trees to logical forms.
Example \ref{ex:nobel} shows an example abstract syntax tree and its
realisation in English.

@@

This temporal context is an \emph{optional} timespan. That is, it can
be a timespan or an explicitly unspecified context.
\newcommand\nospan{\ensuremath{-}}
\newcommand\anyspan{\ensuremath{\mathbf{*}}} The timespan in the context is
optional because, in certain situations, the semantics is different
depending on whether a timespan has been specified externally or not,
as we explain below. A non-present timespan will be represented as
\nospan{}. If a semantic function does not depend on the temporal
context at all, we will write \anyspan{} instead.

@@

\newcommand\varid[1]{\mathnormal{#1}}
%
The principal non-trivial manipulators of timespans are tense
markers. In our syntax, inherited from GF, tenses are represented
syntactically as an attribute of clauses. An illustration of a
past-tense clause and its interpretation follows in
Example \ref{ex:nobel}. Notice in particular the $\varid{past}$ argument to
the $\varid{useCl}$ constructor.
